Verifying Demonstrations

### 2018-05-30 paper/DistanceBounding.tex
Changes notation from DBPK to PPK (fixes #110)

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{DBPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{DBPK} (\eg that it must be \iac{PKE} for discrete logarithms).

>>>>

The majority of the existing \ac{DB} protocols are symmetric and thus requires an honest verifier.
Indeed, in this context it does not make sense to protect against the verifier as he can easily impersonate the prover as he has a knowledge of his secret key.
There has been less work done in the domain of asymmetric (or public-key) \ac{DB} protocols.
Unfortunately, our setting requires a public-key \ac{DB} protocol with a \emph{malicious verifier} who will try to \emph{impersonate the prover}.
The verifier might also try to track the provers and map their identities to their actions, thus we also require privacy.
This leads to the requirement of a \ac{DB} \ac{ZKPK}, or simply \ac{PPK}, with resistance to all the frauds mentioned above as well as against this verifier who will attempt to impersonate the prover.
More specifically, we must combine such \iac{DB} with anonymous credentials (which we do in \cref{DB-anon-cred}).
The choice of the anonymous credential system will affect the properties we require of the \ac{PPK} (\eg that it must be \iac{PKE} for discrete logarithms).

### 2018-05-30 paper/analysis-security.tex
Fixes typo: g_T^{\sk+x} -> g_T^{1/(\sk+x)}
Adds Jane to security analysis too
Changes notation from DBPK to PPK (fixes #110)

There is also another case of collision that we must prevent.
Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and 
witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, \eg 
\(\pid = \AC[PRF]_{\sk}(x)\) but \(\wid = \AC[\overline{PRF}]_{\sk}(x)\).

@@

However, say that a witness works for Grace.
This witness interacts with Alice directly, \ie has (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
and to verify the \ac{DBPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
  witness in the \ac{DBPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.

>>>>

There is also another case of collision that we must prevent.
Consider that Alice computes \(\pid = \ACprf[_\sk][\cid]\) for some cause 
identifier \(\cid\) and some witnesses computes \(\wid_1, \dotsc, \wid_n\), 
with \(\wid_i = \ACprf[_{\sk_i}][\pid]\).
Now, if Alice would construct a manifesto \(m\) such that \(\Hash[m] = \pid\), 
then \(\wid_1, \dotsc, \wid_n\) would be valid participant identifiers for the 
protest with manifesto \(m\).
This means that we must separate the mechanisms used for participating and 
witnessing.
The protocol achieves this by the fact that \[
  \prf_{\wid} = \SPK[\sk_i][\dotsc][\pid, \wid, t_s, t_s', l]
\]
does not include \(\cid\) whereas \[
  \prf_{\pid} = \SPK[\sk_i][\dotsc][\cid, \pid, \wid, t_s, t_s', l]
\]
does.
Thus the verification process differs for the two types of proofs.
(An alternative approach would have been to compute them differently, \eg 
\(\pid = \AC[PRF]_{\sk}(x) = g_T^{1/(\sk+x)}\) but \(\wid = 
  g_T^{1/(\sk+x+1)}\).)

@@

However, say that a witness works for Grace.
This witness interacts with Alice directly, \ie has (physically) identified her.
The witness also learns Alice's \(\pid\), but not \(\cid\), to compute \(\wid\) 
and to verify the \ac{PPK}.
\daniel{This assumes that I will do the changes to hide \(\cid\) from the 
  witness in the \ac{PPK}.}
Afterwards, Alice publishes \(\pid\) and \(\cid\) together as part of the proof 
share.
The probability of a colliding \(\pid = \ACprf[_\sk][\cid']\) for some \(\cid' 
  \neq \cid\) and \(\sk \neq \sk_P\) is \enquote{small}.
\daniel{Fix this.}
Now Grace can link \(\cid\) (and thus the opinions in the manifesto) to Alice.

### 2018-05-30 paper/protocol.tex
Changes notation from DBPK to PPK (fixes #110)

\begin{figure}
  \centering
  \footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
    key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
    \(\sk_W\) and \(\pid\).
    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
    witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of 
    \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  \footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \DBPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\rgets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(\pid\).)
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{DBPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \mleftright
  \DBPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{DBPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(\wid\gets 
  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Then the witness returns \((\wid, t_s', l)\) to the participant.
Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
  t_s, t_s', l)\) which constitutes a proof share of the participant 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the participant uploads the tuple \[
  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
\] for permanent storage.
\daniel{Return \(\pi'\), whatever that should be.}

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
\] for permanent storage.
\daniel{Return \(\pi''\), whatever that should be.}

>>>>

\begin{figure}
  \centering
  %\footnotesize
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's 
    key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s identifier \(\wid\) is computed using the witness's key 
    \(\sk_W\) and \(\pid\).
    \(t_s, t_s'\) are the last head of the blockchain seen by the protester and 
    witness, respectively, and \(l\) is an area.
    All values are signed by the witness while also proving the correctness of 
    \(\wid\) and knowledge of a signature on \(\sk_W\).
  }%
  \label{fig:ProofFig}
\end{figure}%

\begin{figure}
  \centering
  %\footnotesize
  \begin{minipage}{\linewidth}
    \begin{align*}
      O\to \text{all}\colon & \text{manifesto} \\
      P\colon & t_s\gets \TSget \\
        & \cid\gets \Hash[\text{manifesto}], \\
        & \pid\gets \ACprf[_{\sk_P}][\cid] \\
      W\colon & t_s'\gets \TSget
      \\[-1em]
      \noalign{\hfill Join}
      \midrule
      \noalign{\hfill Participation}
      \\[-3em]
      P\to W\colon & \pid \\
      P\leftrightarrow W\colon &
        \PPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
      W\colon & \wid\gets \ACprf[_{\sk_W}][\pid] \\
      W\to P\colon & (\wid, t_s', l)
      \\[-1em]
      \noalign{\hfill Participation}
      \midrule
      \noalign{\hfill Submission}
      \\[-2em]
      P\colon & t_e\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\colon & t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]] \\
      W\to S\colon & (\pid, \wid, t_s, t_s', t_e, l, \pi_{\wid}),\quad 
      \text{where} \\
        & \pi_{\wid} = \SPK\mleft\{ (\sk_W) : \mright. \\
        & \qquad \wid = \ACprf[_{\sk_W}][\pid], \\
        & \qquad \mleft. \sigma_W' = \ACblind[\ACsign[_{\ssk}][\sk_W]]\mright\} 
        \\
        & \qquad\qquad (\pid, \wid, t_s, t_s', l) \\
      P\to S\colon & (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid}),\quad 
      \text{where}\\
        & \pi_{\pid} = \SPK\mleft\{ (\sk_P) : \mright. \\
        & \qquad \pid = \ACprf[_{\sk_P}][\cid], \\
        & \qquad \mleft. \sigma_P' = \ACblind[\ACsign[_{\ssk}][\sk_P]] \mright\} 
        \\
        & \qquad\qquad (\cid, \pid, \wid, t_s, t_s', l)
    \end{align*}
  \end{minipage}
  \caption{%
    An overview of of the Join, Participation and Submission phases of \PRIVO.\@
    The organizer \(O\) broadcasts the manifesto.
    The protester \(P\), witness \(W\) and their computations are as in 
    \cref{fig:ProofFig}.
    Finally, both \(P\) and \(W\) submits the proof share to some permanent 
    storage \(S\).
  }%
  \label{fig:ProtocolOverview}
\end{figure}

@@

\emph{Participating: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participating phase the participant and the witness constructs the proof 
share of the participant (\cref{fig:ProofFig}).
The participant reblinds its signature \(\sigma\) on its secret key: choose 
\(r_1, r_2\rgets \ZZ_q^*\) and let \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) (It is not necessary to compute a new \(\tilde\sigma\) more than once per 
\(\pid\).)
The participant sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the participant and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Then they run the following \ac{PPK} with the participant as the prover and the 
witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k+\cid)} \right\}.
\end{multline*}
where \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Then the \ac{PK} can be designed as follows (remember that this \ac{PK} should 
be run as \iac{PPK} and be repeated multiple times to achieve security).
The participant chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly randomly, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
The participant then computes
\begin{align*}
s_k &= -ck + r_k, \\
s_r &= -cr + r_r, \\
s_{r'} &= cr' + r_{r'}
\end{align*}
and sends them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds the witness will compute \(\wid\gets 
  \ACprf[_{\sk_W}][\pid] = g_T^{1/(k_W+\pid)}\) (as above).
Then the witness returns \((\wid, t_s', l)\) to the participant.
Now both the participant and the witness have the tuple \(\pi = (\pid, \wid, 
  t_s, t_s', l)\) which constitutes a proof share of the participant 
(\cref{fig:ProofFig}).

@@

\emph{Submission: \(\pi'\gets \PRIVOsubmit[_P][\cid, \pid, \wid, t_s, t_s', 
    l]\).}
The participant should as soon as possible commit the proof-share data to the 
time-stamping service and receive the proof of commitment, \(t_e\gets 
  \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
The remaining operations are not time critical.
The participant computes \iac{NIZK} proof \(\pi_{\pid}\) which shows the 
correctness of \(\pid\).
More specifically,
\begin{multline*}
  \pi_{\pid}\gets \SPK\left\{ (\sk_P) : \right. \\
    \begin{aligned}
      \pid &= \ACprf[_{\sk_P}][\cid] \quad \land \\
      \sigma_P' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_P]] \right\}
    \end{aligned} \\
      (\cid, \pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the participant uploads the tuple \[
  (\cid, \pid, \wid, t_s, t_s', t_e, l, \pi_{\pid})
\] for permanent storage.
\daniel{Return \(\pi'\), as specified as output.}

\emph{Submission: \(\pi''\gets \PRIVOsubmit[_W][\pid, \wid, t_s, t_s', l]\).}
The witness should, just as the participant, commit the proof-share data to the 
time-stamping service, \(t_e'\gets \TSstamp[\Hash[\pid, \wid, t_s, t_s', l]]\).
(This is for redundancy only.)
Then, without any time requirements, the witness computes \iac{NIZK} proof 
\(\pi_{\wid}\) as follows:
\begin{multline*}
  \pi_{\wid}\gets \SPK\left\{ (\sk_W) : \right. \\
    \begin{aligned}
      \wid &= \ACprf[_{\sk_W}][\pid] \quad \land \\
      \sigma_W' &= \left. \ACblind[\ACsign[_{\ssk}][\sk_W]] \right\}
    \end{aligned} \\
      (\pid, \wid, t_s, t_s', l).
\end{multline*}
Finally, the witness uploads the tuple \[
  (\pid, \wid, t_s, t_s', t_e', l, \pi_{\wid})
\] for permanent storage.
\daniel{Return \(\pi''\), as specified as output.}
